Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-10-20 Report/convergence_centralized.tex
updated convergence proof

To prove the convergence of the transmit, receive beamformers, and the objective values of the centralized algorithms in \eqref{eqn-6} and \eqref{eqn-mse-1}, we will show that the following conditions are satisfied by the centralized formulations.
\begin{itemize}
	\item[(a)] The function should be bounded below
	\item[(b)] The feasible set should be a compact set
	\item[(c)] The sequence of the objective values should be \review{strictly} decreasing in each iteration
	\item[(d)] Uniqueness of the minimizer, \textit{i.e.}, the transmit and the receive beamformers should be unique in each iteration.
\end{itemize}
The conditions (a) (b) and (c) are required for the convergence of the objective values generated by the iterative algorithm. Since the feasible set is not fixed in each iteration, we require the condition (d) to prove the convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders to a stationary point \cite{meyer1976sufficient}. Assuming the conditions (a), (b) and (c) are satisfied, using \cite[Th. 3.14]{rudin1964principles}, we can show that the bounded and strictly decreasing objective sequence has a unique minimum in the feasible set. Finally, we use the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1} to show that the limit point of the iterative algorithm is indeed a stationary point of the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.

@@

To solve \eqref{con}, we adopt \ac{AO} by fixing a block of variables and optimize for others \cite{bezdek2002some}. However, after fixing the variable \me{\my}, the problem is still nonconvex due to the constraint \eqref{con-dc}. To overcome this issue, we resort to \ac{SCA} principle presented in \cite{lanckriet2009convergence,scutari_1,scutari-1} by relaxing \eqref{con-dc} by a sequence of convex subsets. Since it involves two nested iterations, we denote the \ac{AO} step by a superscript \me{(i)} and the \ac{SCA} iteration by a subscript \me{k}. Let \me{\iter{\mx}{\ast}{i}} be the value of \me{\mx} when \ac{SCA} converges in the \me{\ith{i}} \ac{AO} step and let \me{\iter{\mz}{\ast|\my}{i}} be the solution for \me{\mz} in the \me{\ith{i}} \ac{AO} step for fixed \me{\my}. The stacked transmit precoders of all users in the \eqn{\ith{k}} \ac{SCA} step of the \eqn{\ith{i}} \ac{AO} is given by \eqn{\mx_k^{(i)}}.

\subsection{Bounded Objective Function and Compact Feasible Set}
The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which is verified by the total power constraint on the transmit precoders \eqref{eqn-6.4}, therefore, the sets are compact.

@@

\subsection{Uniqueness of the Iterates and Strong Convexity} \label{c-a}
The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}\}} can be ensured for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active. However when \eqn{\hat{f}(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness cannot be guaranteed as there can be multiple solutions with the same objective value in the feasible set. Similarly, when the objective is non-zero for \eqref{eqn-9}, the minimizer is unique only if the receivers are matched to the transmit beamformers. %, \textit{i.e.}, \me{q_{l,k,n} = 0} in \eqref{eqn-wsrm-expr}, while initializing the feasible point \eqn{\iter{\mx}{0}{0}} and \eqn{\iter{\my}{0}{0}}.

\review{To ensure the uniqueness of the transmit and the receive beamformers, the objective function of the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + {\tau}_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is a vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem. The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures the strong convexity of \eqn{f} in each step and \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, as shown in \cite{scutari-1}. Thus, due to the strong convexity of \eqn{f} in \eqref{mod_obj}, the uniqueness of the minimizer can be guaranteed in each \ac{SCA} step as discussed in \cite{yang_yang,scutari-1}. The quadratic term in \eqref{mod_obj} includes the earlier solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, obtained by solving \eqref{eqn-9} or \eqref{eqn-mse-2} in the \eqn{\ith{(k-1)}} \ac{SCA} step.}

@@

\subsection{Strict Monotonicity of the Objective Sequence} \label{mcity}
\review{In the forthcoming discussions, we consider the modified objective \eqn{f} in \eqref{mod_obj} instead of \eqn{\hat{f}} due to the uniqueness property. Note that the modified objective \eqn{f} is equivalent to \eqn{\hat{f}} upon convergence, \textit{i.e.}, when the solution is a limit point. Therefore, the discussions are valid for the \ac{JSFRA} problem in \eqref{eqn-6} by regularizing the original objective \eqref{eqn-6.1} as \eqref{mod_obj}.}

To begin with, let us consider the variable \me{\my} is fixed for the \me{\ith{i}} \ac{AO} with the optimal value found in previous iteration \me{i-1} as \me{\iter{\my}{\ast}{i-1}}. In order to solve for \me{\mx} in \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate \me{\iter{\mx}{k}{i}} of \me{\mx} as

@@

\hat{g}_o(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) = {g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1}) + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).

@@

\hat{g}_o(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) = {g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1}) \\ + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).

@@

Let \me{\iter{\mc{X}}{k}{i}} be the feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\iter{\my}{\ast}{i-1}} and \me{\iter{\mx}{k}{i}}. Similarly, \me{\iter{\mc{Y}}{k}{i}} denotes the feasible set for a fixed \me{\iter{\mx}{\ast}{i}} and \me{\iter{\my}{k}{i}}. Using \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for the variable \me{\mx} and \me{\mz} is given by

@@

	\underset{\mx,\mz}{\text{minimize}} &\quad& f(\mx,\iter{\my}{\ast}{i-1},\mz) \eqsub \label{con-obj-m} \\
	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0 \eqsub \label{con-dc-m} \\
	&\quad& g_1(\mx,\iter{\my}{\ast}{i-1}) \leq 0, \quad g_2(\mx) \leq 0 \eqsub \label{con-cvx-blk-m}

@@

h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}) \leq h(\iter{\mz}{k+1}{i}) - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0. 

@@

h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}) \leq \\
h(\iter{\mz}{k+1}{i}) - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0. 

@@

Using \eqref{con-sub-set}, we can show that \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}, \iter{\mz}{k+1}{i}\}} is feasible, since the initial \ac{SCA} operating point \me{\iter{\mx}{\ast}{i-1}} was chosen to be feasible from the \me{\ith{(i-1)}} \ac{AO} iteration. In each \ac{SCA} step, the feasible set includes the solution from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, therefore, it decreases the objective as \cite{lanckriet2009convergence,scutari_1,amir}

@@

f(\iter{\mx}{0}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}) \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}). 

@@

f(\iter{\mx}{0}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}) \\ \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}). 

@@

Thus, the sequence \me{\{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})\}} is nonincreasing. \review{Since the objective is strongly convex due to the introduced quadratic term in \eqref{mod_obj}, the minimizer \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}\}} in each \ac{SCA} step is unique. Now, by using the fact that the objective sequence is nonincreasing and the uniqueness of the minimizer in each convex subproblem \eqref{con-m}, we can ensure that the sequence of iterates generated by the iterative \ac{SCA} approach converges to a unique limit point in each \ac{AO} step \eqn{{i}}}. 
	%However, note that the limit point need not be a stationary point of \eqref{con}, since the receive equalizers \eqn{\my} have been fixed.}

% and approaches limit point of the \ac{SCA} as \me{k \rightarrow \infty}. The equality in \eqref{con-convergence} is achieved upon the \ac{SCA} convergence. The limit point obtained in the \eqn{\ith{i}} \ac{AO} step need not to be a stationary point of \eqref{con}, since it is the minimizer in \me{\iter{\mc{X}}{\ast}{i}} only. \review{Note that for a fixed initial operating point of the iterative \ac{SCA} procedure, the minimizer in each \ac{SCA} step is unique and so the limit point due to the strong convexity of the modified objective \eqref{mod_obj}.}

%\review{Since the objective is strongly convex, due to the quadratic term in \eqref{mod_obj}, the minimizer \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} in each \ac{SCA} step is unique.}

Once \me{\iter{\mx}{\ast}{i}} is found for fixed \me{\my}, then \eqref{con} is solved for \me{\my} with fixed \me{\mx}. However, after fixing \me{\mx} as \me{\iter{\mx}{\ast}{i}} in \eqref{con}, the problem is still nonconvex due to \eqref{con-dc}. Following similar approach as above, the minimizer \me{ \{\iter{\mx}{\ast}{i},\iter{\my}{k+1}{i},\iter{\mz}{k+1}{i}\}} can be found in each \ac{SCA} step \me{k} by solving \eqref{con-m} iteratively. Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration. The sequence convergence and the nonincreasing behavior of the objective follow similar arguments as above. \footnote{Note that the \ac{MMSE} receiver in \eqref{eqn-10} can also be used instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The limit point of the sequence of iterates generated by iteratively solving \eqref{con-m} is given by \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\} \in \iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.

Finally, to prove the global convergence of the iterative algorithm, we need to show that the \ac{AO} updates also produce a nonincreasing sequence of objectives, \textit{i.e.}, 
\iftoggle{single_column}{
\begin{equation}
f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
\end{equation}}{
\begin{equation}
f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
\end{equation}}
Let \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mz}{\ast|\my}{i}} be the solution obtained by solving \eqref{con-m} iteratively until \ac{SCA} convergence in the \me{\ith{i}} \ac{AO} iteration for \eqn{\mx} and \eqn{\mz} with fixed \eqn{\my = \iter{\my}{\ast}{i-1}}. To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}. Since the convex function is linearized in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \iter{\mc{Y}}{0}{i}} by the equality in \eqref{con-sub-set}. Using this, we can show the monotonicity of the objective as
\begin{equation} \label{fixed_point}
f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\mx}{i}).
\end{equation}
The \ac{AO} update follows \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}.

>>>>

To prove the convergence of the transmit, receive beamformers, and the objective values of the centralized algorithms in \eqref{eqn-6} and \eqref{eqn-mse-1}, we will show that the following conditions are satisfied by the centralized formulations.
\begin{itemize}
	\item[(a)] The function should be bounded below
	\item[(b)] The feasible set should be a compact set
	\item[(c)] The sequence of the objective values should be \review{strictly} decreasing in each iteration
	\item[(d)] Uniqueness of the minimizer, \textit{i.e.}, the transmit and the receive beamformers should be unique in each iteration.
\end{itemize}
The conditions (a) (b) and (c) are required for the convergence of the objective values generated by the iterative algorithm. Since the feasible set is not fixed in each iteration, we require the condition (d) to prove the convergence of the objective function by enforcing unique transmit precoders and receive beamformer in each step of the iterative algorithm. Assuming conditions (a), (b) and (c) are satisfied, using \cite[Th. 3.14]{rudin1964principles}, we can show that the bounded and strictly decreasing objective sequence has a unique minimum in the feasible set. Finally, we use the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1} to show that \reviewF{every limit point of a convergent subsequence is a stationary point of the nonconvex problem} in \eqref{eqn-6} and \eqref{eqn-mse-1}, since the compact feasible set can have multiple limit points \cite{bertsekas1999nonlinear}.

@@

To solve \eqref{con}, we adopt \ac{AO} by fixing a block of variables and optimize for others \cite{bezdek2002some}. However, after fixing the variable \me{\my}, the problem is still nonconvex due to the constraint \eqref{con-dc}. To overcome this issue, we resort to \ac{SCA} principle presented in \cite{lanckriet2009convergence,scutari_1,scutari-1} by relaxing \eqref{con-dc} by a sequence of convex subsets. Since it involves two nested iterations, we denote the \ac{AO} step by a superscript \me{(i)} and the \ac{SCA} iteration by a subscript \me{k}. Let \me{\iter{\mx}{k}{i}} and \me{\iter{\mz}{k|\my}{i}} be a solution for stacked \me{\mx} and \me{\gamma} obtained in the \eqn{\ith{k}} \ac{SCA} step and in the \eqn{\ith{i}} \ac{AO} step for fixed \me{\my}. Let \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{|\my}{i}} be a solution obtained for \me{\mx} and \me{\gamma} when the objective sequence converges in \eqn{\ith{i}} \ac{AO} step.

\subsection{Bounded Objective Function and Compact Feasible Set} \label{b_obj}
The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which is verified by the total power constraint on the transmit precoders \eqref{eqn-6.4}, therefore, the sets are compact.

@@

\subsection{Uniqueness of the Iterates and Strong Convexity} \label{c-a}
%The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\lpointx}{i-1},\iter{\mz}{k|\my}{i}\}} can be ensured for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active. However when \eqn{\hat{f}(\iter{\mx}{k}{i},\iter{\my}{\lpointx}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness cannot be guaranteed as there can be multiple solutions with the same objective value in the feasible set. Similarly, when the objective is non-zero for \eqref{eqn-9}, the minimizer is unique only if the receivers are matched to the transmit beamformers. %, \textit{i.e.}, \me{q_{l,k,n} = 0} in \eqref{eqn-wsrm-expr}, while initializing the feasible point \eqn{\iter{\mx}{0}{0}} and \eqn{\iter{\my}{0}{0}}.

\review{To ensure the uniqueness of the transmit and the receive beamformers, the objective function of the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
	\hat{f}(\mbf{x}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
	f(\mbf{x}) &=& \hat{f}(\mbf{x}) + {\tau}_k^{(i)} \, \| \mbf{x} - \mbf{x}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{x}} is a vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the problem and \eqn{\mbf{x}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is the solution obtained in the previous \eqn{\ith{(k-1)}} \ac{SCA} step. The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures the strong convexity of \eqn{f} in each step and \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, as shown in \cite{scutari-1}. Thus, due to the strong convexity of \eqn{f} in \eqref{mod_obj}, uniqueness of the minimizer is guaranteed in each \ac{SCA} step as discussed in \cite{yang_yang,scutari-1}}.

@@

\subsection{Strict Monotonicity of the Objective Sequence} \label{mcity}
\review{In the following discussions, we consider the modified objective \eqn{f} in \eqref{mod_obj} instead of \eqn{\hat{f}} due to the uniqueness of the minimizer and upon convergence of the objective, \eqn{f} is equal to \eqn{\hat{f}}. Therefore, the discussions are valid for the \ac{JSFRA} problem in \eqref{eqn-6} by regularizing the objective \eqref{eqn-6.1} as \eqref{mod_obj}.}

To begin with, let us consider the variable \me{\my} is fixed for the \me{\ith{i}} \ac{AO} with the optimal value found in previous iteration \me{i-1} as \me{\iter{\my}{\lpoint}{i-1}}. In order to solve for \me{\mx} in \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate \me{\iter{\mx}{k}{i}} of \me{\mx} as

@@

\hat{g}_o(\mx,\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) = {g}_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1}) + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).

@@

\hat{g}_o(\mx,\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) = {g}_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1}) \\ + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).

@@

Let \me{\iter{\mc{X}}{k}{i}} be the feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\iter{\my}{\lpoint}{i-1}} and \me{\iter{\mx}{k}{i}}. Similarly, \me{\iter{\mc{Y}}{k}{i}} denotes the feasible set for a fixed \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\my}{k}{i}}. Using \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for the variable \me{\mx} and \me{\mz} is given by

@@

	\underset{\mx,\mz}{\text{minimize}} &\quad& f(\mx,\iter{\my}{\lpoint}{i-1},\mz) \eqsub \label{con-obj-m} \\
	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) \leq 0 \eqsub \label{con-dc-m} \\
	&\quad& g_1(\mx,\iter{\my}{\lpoint}{i-1}) \leq 0, \quad g_2(\mx) \leq 0 \eqsub \label{con-cvx-blk-m}

@@

h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1}) \leq h(\iter{\mz}{k+1}{i}) - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) \leq 0. 

@@

h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1}) \leq \\
h(\iter{\mz}{k+1}{i}) - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) \leq 0. 

@@

Using \eqref{con-sub-set}, we can show that \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1}, \iter{\mz}{k+1}{i}\}} is feasible, since the initial \ac{SCA} operating point \me{\iter{\mx}{\lpoint}{i-1}} was chosen to be feasible from the \me{\ith{(i-1)}} \ac{AO} iteration. In each \ac{SCA} step, the feasible set includes the solution from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, therefore, it decreases the objective as \cite{lanckriet2009convergence,scutari_1,amir}

@@

f(\iter{\mx}{0}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k}{i}) \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}). 

@@

f(\iter{\mx}{0}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k}{i}) \\ \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}). 

@@

Thus, the sequence \me{\{f(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k}{i})\}} is nonincreasing. %\review{Since the objective is strongly convex due to the introduced quadratic term in \eqref{mod_obj}, the minimizer \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k}{i}\}} in each \ac{SCA} step is unique. Now, by using the fact that the objective sequence is nonincreasing and the uniqueness of the minimizer in each convex subproblem \eqref{con-m}, we can ensure that the sequence of iterates generated by the iterative \ac{SCA} approach converges to a unique limit point in each \ac{AO} step \eqn{{i}}}. 
\review{However, to ensure strict monotonicity of the objective sequence, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some parameter \eqn{c > 0}. Now, to show strict monotonicity, let us consider \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} as the minimizer for \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} step. At the \eqn{\ith{k}} \ac{SCA} iteration, \eqn{\forall \mbf{z} \in \mc{X}_{k}^{(i)}}, it follows
\begin{IEEEeqnarray}{rCl} \neqsub \label{strict_monotonicity}
\nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z} - \iter{\mbf{z}}{k+1}{i}) &\geq& 0 \eqsub \\
f(\mbf{z}) - f(\iter{\mbf{z}}{k+1}{i}) &\geq& c \, \|\mbf{z} - \iter{\mbf{z}}{k+1}{i}\|^2 \eqsub
since \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}. Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}. Now, by using the fact that the objective sequence is strictly nonincreasing and bounded, we can ensure the convergence of the objective sequence in each \ac{AO} step \eqn{{i}}} and \reviewF{\eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} is the unique solution obtained upon the convergence of the objective sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} in the \eqn{\ith{i}} \ac{AO} iteration.}

Once \me{\iter{\mx}{\lpoint}{i}} is obtained for fixed \me{\my}, then \eqref{con} is solved for \me{\my} with fixed \me{\mx}. However, after fixing \me{\mx} as \me{\iter{\mx}{\lpoint}{i}} in \eqref{con}, the problem is still nonconvex due to \eqref{con-dc}. Following similar approach as above, the minimizer \me{ \{\iter{\mx}{\lpoint}{i},\iter{\my}{k+1}{i},\iter{\mz}{k+1}{i}\}} can be found in each \ac{SCA} step \me{k} by solving \eqref{con-m} iteratively. Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration. The convergence and the nonincreasing behavior of the objective follow similar arguments as above. \footnote{Note that the \ac{MMSE} receiver in \eqref{eqn-10} can also be used instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The solution obtained by solving \eqref{con-m} iteratively until convergence of the objective value is given as \me{\{\iter{\mx}{\lpoint}{i}, \iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|\mx}{i}\} \in \iter{\mc{Y}}{\lpoint}{i} \subset \mc{F}}.

Finally, to prove the global convergence of the \reviewF{objective sequence}, we need to show that the \ac{AO} updates also produce a nonincreasing sequence of objectives, \textit{i.e.}, 
\iftoggle{single_column}{
\begin{equation}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}}{
\begin{equation}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}}
Let \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\mz}{\lpoint|\my}{i}} be the solution obtained by solving \eqref{con-m} iteratively until \ac{SCA} convergence in the \me{\ith{i}} \ac{AO} iteration for \eqn{\mx} and \eqn{\mz} with fixed \eqn{\my = \iter{\my}{\lpoint}{i-1}}. To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\lpoint}{i}} and optimize for \me{\my}. Since the convex function is linearized in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \iter{\mc{Y}}{0}{i}} by the equality in \eqref{con-sub-set}. Using this, we can show the monotonicity of the objective as
\begin{equation} \label{fixed_point}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\mx}{i}).
\end{equation}
The \ac{AO} update follows \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \{ \iter{\mc{X}}{\lpoint}{i} \cap \iter{\mc{Y}}{0}{i} \}}.

\review{Using \eqref{strict_monotonicity}, strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update can also be ensured. It follows from that fact that \eqn{\iter{\mbf{z}}{\lpoint}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} update.}
\begin{comment}
\begin{equation} \label{strict_monotonicity}
f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) \geq \nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}) + \frac{m}{2} \, \|\mbf{z}_{k+1}^{(i)} - \iter{\mbf{z}}{k}{i}\|^2  \eqspace
\end{equation}
